### 2014-07-23 MS.tex
legend fig 1

\texttt{Figure 1.} Results of the MEDUSA analysis run on the maximum
clade credibility tree from Reference 10. Rate shifts were estimated for
the following nodes (besides the background rate): 2) Limenitidinae +
Heliconiinae, 3) \emph{Ypthima}, 4) \emph{Charaxes}, 5) Ithomiini in
part, 6) Satyrini, 7) Coenonymphina 8) Phyciodina in part, 9) Danaini in
part, 10) \emph{Coenonympha}, 11) \emph{Caeruleuptychia} +
\emph{Magneuptychia}, 12) \emph{Callicore} + \emph{Diaethria}, 13)
Satyrina, 14) Mycalesinaa, 15) \emph{Pedaliodes}, 16) \emph{Dryas} +
\emph{Dryadula}, 17) \emph{Taenaris}, 18) Pseudergolinae.

>>>>

\texttt{Figure 1.} Results of the MEDUSA analysis run on the maximum
clade credibility tree from Reference 10. Estimated rate shifts in Table 1.
